---
title: "Tarea Anova"
output:
  pdf_document: default
  html_notebook: default
---
Alfonso Fajardo 
### ejercicio 8.2.4

Gold et al. (A-5) investigated the effectiveness on smoking cessation of a nicotine patch, bupropion
SR, or both, when co-administered with cognitive-behavioral therapy. Consecutive consenting
patients ð Þ n ¼ 164 assigned themselves to one of three treatments according to personal preference:
nicotine patch NTP ð Þ ; n ¼ 13 , bupropion SR B ð Þ ; n ¼ 92 , and bupropion SR plus nicotine patch
ð Þ BNTP; n ¼ 59 . At their first smoking cessation class, patients estimated the number of packs of
cigarettes they currently smoked per day and the numbers of years they smoked. The "pack years" is
the average number of packs the subject smoked per day multiplied by the number of years the subject
had smoked. The results are shown in the following table.

## importar los datos y asignar la variable  en factor
```{r}

smoke_data <- read.csv("ch08_all/EXR_C08_S02_04.csv")
smoke_data$GROUP <- as.factor(smoke_data$GROUP)
levels(smoke_data$GROUP) <- c("patch","Bup","patch+Bup")
```
## boxplot
```{r}
library("ggplot2")

ggplot(data = smoke_data, mapping = aes(x= GROUP, YEARS,col = GROUP))+
  geom_boxplot()+
  geom_jitter(height = 0.01,width = 0.1 )


```
```{r}
library(MASS)
truehist(smoke_data$YEARS, nbins=9, col = "salmon")
lines(density(smoke_data$YEARS),lty=2,col="blue",lwd=3)
```

## Test de normailidad


```{r}
shapiro.test(smoke_data$YEARS)
```

## test de varianzas
```{r}
library(car)
leveneTest(YEARS~GROUP,data = smoke_data)
```
## Anova
```{r}
lm_smoke<- lm(YEARS~GROUP, data = smoke_data)
aov_smoke <- aov(lm_smoke)
anova(aov_smoke)
                     
```
# Poshoc
```{r}
 TukeyHSD(aov_smoke)
plot(TukeyHSD(aov_smoke))

```

